A parallelised and distributed approach to implementing Conway's Game of Life

### 2022-12-06 report/article_2.tex
Added fault tol report

@@

\section{benchmarking and critical analysis of enabling SDL}
% i dont think we need benchmarking of SDL
% \lettrine[nindent=0em,lines=3]{L} orem ipsum dolor sit amet, consectetur adipiscing elit.
\begin{itemize}
  \item show graphs and describe shape and differences of with vs without SDL
  \item explain how SDL works
  \item explain how this causes bottlenecks
\end{itemize}
%------------------------------------------------

>>>>

\section{Friends? - Multi-worker GoL}
\subsection{Implementing multiple workers}
With the introduction of multiple workers, we needed to introduce a broker to interface the workers for the controller
and vice versa. This did require moving turn iteration logic to the broker, requiring a major refactor. In the end, the system
revolved around the broker with bidirectional RPC communication betweeen workers and the controller. We equally divide work
between workers, and all processes keep an internal state of some sort. By massively simplifying, the broker does the following:

\begin{enumerate}[noitemsep]
  \item Listen for worker and controller connections
  \item On connect, call the worker/controller back (bidirectional)
  \item Listen for GoL process request from controller
  \item Iterate, dividing and sending work to each worker.
  \item After getting all parts back together, apply changes to broker internal state and divide new state up
\end{enumerate}
%--------------
\begin{itemize}
  \item ADD BENCHMARKS HERE
\end{itemize}
%--------------
\subsection{Analysis 5}
%--------------
\begin{itemize}
  \item ADD ANALYSIS HERE
  \item explain trends, averages, maybe std dev?
  \item if low std dev then time not affected too much by worker count
\end{itemize}
%--------------
\section{Tolerating faults}
\subsection{Managing workers}
In our previous implementation, we never checked for worker disconnects. This leaves us in a vulnerable
position - if a worker were to be terminated at any point, then we would have one section of changes missing.
This would show itself with a static portion on the SDL window. There is also the case of adding more workers. Either
way, it means we need to keep the order of workers. We present Algorithm 3 to solve this.
\begin{algorithm}
  \caption{Worker-diff checker}
  \begin{algorithmic}
    \State Require $ids \subseteq \mathbb{N}$
    \State Require $oldIds \subseteq \mathbb{N}$ 
    \State Let $idMap \gets Map$
    \For{$id \in ids$}
      \State $idMap[id] \gets addr$
    \EndFor
  \For{$id \in oldIds$}
      \If{idMap[id] = nil}
      \State \Return False
      \EndIf
    \EndFor
    \State \Return True
  \end{algorithmic}
\end{algorithm}

What this algorithm achieves is detection of disconnects and reconnects.
Given that we have the loop invariant (in turn iterator) "no two workers will have the same worker id",
we can use this algorithm, and if we detect a change, recalibrate the workers to adjust for new/missing worker. 
One may ask, does a worker disconnect not throw errors when calling RPC methods? In this case, we utilise \texttt{client.Go},
which notifies the calling process of errors without crashing. So, if error, then trigger recalibration.

@@
